%!TEX root = ../report.tex
\clearpage
\chapter{Introduction}
\label{ch:introduction}
This document presents architecture recovery of
Docker\footnote{\url{https://www.docker.com/}} by identifying software patterns
and performing an evaluation of the architecture based on the identified
patterns. This document is part of the Software Pattern assignment at the
University of Groningen.

Docker is an open-source project that automates the deployment of applications
inside software containers, by providing an additional layer of abstraction and
automation of operating-system-level virtualization on Linux \cite{dockerdef}.
Docker can also run on Windows and Mac OSX, although it is actually run through
a VM using Docker Machine because Docker Engine itself can only run on Linux.

The structure of the document is explained as follows. Chapter \ref{ch:context}
gives brief explanation with regard to Docker. Chapter \ref{ch:stakeholders}
elaborates on the stakeholders involved in the Docker project and its
corresponding key-drivers. Chapter \ref{ch:softwarearch} depicts the
architecture of Docker using logic and process views to make it more clear.
Patterns discovered in the Docker project are documented in chapter
\ref{ch:patterns}. Evaluation is presented in chapter \ref{ch:evaluation}.
Chapter \ref{ch:recommendations} gives several recommendation for the Docker
project. Lastly, a conclusion is drawn in chapter \ref{ch:conclusion}.

This project utilizes the IDAPO\footnote{Identifying Architectural Patterns in
Open Source Software} process to recover the architecture \cite{idapo}. The
PBAR\footnote{Pattern-Based Architecture Reviews} approach is used to perform
the evaluation \cite{pbar}.

There are 12 steps in IDAPO. Those steps are:
\begin{enumerate}
\item identifying the type and domain
\item identifying used technologies
\item studying used technologies
\item identifying candidate patterns
\item reading patterns literature
\item studying the documentation
\item studying the source code
\item studying components \& connectors
\item identifying patterns and variants
\item validating identified patterns
\item getting the feedback from community
\item register pattern usage
\end{enumerate}

Chapter \ref{ch:context} and Chapter \ref{ch:stakeholders} correspond step (1)
of IDAPO. Step (2) to (5) are related to Chapter \ref{ch:softwarearch}, where
used technologies are presented in the architecture. Chapter \ref{ch:patterns}
corresponds to step (6) to (12), where the result of those steps is the pattern
documentation.

While IDAPO recovers the patterns inside Docker, PBAR process determines the
high-level process of pattern-based recovery and the evaluation of the
architecture. The evaluation is documented in Chapter \ref{ch:evaluation}.

%\begin{table}
%\begin{tabular}{c c c}
%a & b & c \\
%d & e & f 
%\end{tabular}
%\caption{test}
%\end{table}